QCL: Added value of differential correlation

### 2011-11-23 inst/doc/article.Rnw
Updates to the paper
Added the stackedHistogram plot, to show the pheno -> marker -> phenotype relations

\emph{\sffamily Preprocessing}

\section*{Algorithm: QCL mapping}

QCL mapping however uses this buffering to detect interaction partners. The hypothesis 
is that when we split the population based on genotype at the cis-marker, related phenotypes 
will loosing correlation with the gene under investigation. This allows us to not only 
only identify its interaction partners. QCL mapping is thus not suffering from (p1) many 
phenotypes co-localizing). Additionally it is more sensitive to detect variation caused by 
regulators genes because variation of these genes causes many 'downstream' phenotypes 
to show differential correlation with the inducing phenotype, because QCL relies on 
correlation changes as opposed to differences in phenotype mean QCL is unaffected by (p2).

@@

\bigskip
\section*{Results}
\nopagebreak

@@

Overview plots of the results of the QCL mapping in Arabidopsis can be found in 
Figure XX Phenotype to Marker interaction, which is comparable to the QTL mapping 
(Fig. XX). The additional information obtained by QCL mapping is shown in a heatmap 
of the Phenotype to Phenotype interaction matrix (figure XX) and the same information 
but now represented as an interaction network is seen in figure XX
\begin{table}[ht]
\begin{tabular}{ l | c c }
P-value & QCL threshold Arabidopsis & QCL threshold Saccharomyces\\
\hline
5 \% & 0.220 & 0.435\\
1 \% & 0.294 & 0.495\\
0.1 \% & 0.375 & 0.562\\
\end{tabular}
\caption{QCL thresholds obtained after 1000 permutations}
\label{permutations}
\end{table}

>>>>

\emph{\sffamily QCL mapping}

QCL mapping uses this buffering to detect interaction partners. The hypothesis 
is that when we split the population based on genotype at the cis-marker, related phenotypes 
will loosing correlation with the gene under investigation. This allows us to not only 
only identify its interaction partners, but also QCL mapping does not suffering from (p1) many 
phenotypes co-localizing. Additionally it is more sensitive to detect variation caused by 
regulators genes because variation of these genes causes many 'downstream' phenotypes 
to show differential correlation with the inducing phenotype, because QCL relies on 
correlation changes as opposed to differences in phenotype mean QCL is unaffected by (p2).

@@

\bigskip
\section*{Results}
\emph{\sffamily Preprocessing}

\nopagebreak

@@

Overview plots of the results of the QCL mapping in Arabidopsis can be found in 
Figure XX Phenotype to Marker interaction, which is comparable to the QTL mapping 
(Fig. XX). The additional information obtained by QCL mapping is shown in a heatmap 
of the Phenotype to Phenotype interaction matrix (figure XX) and the same information 
but now represented as an interaction network is seen in figure XX
\begin{table}[ht]
\begin{tabular}{ l | c c }
P-value & QCL threshold Arabidopsis & QCL threshold Saccharomyces\\
\hline
5 \% & 0.220 & 0.436\\
1 \% & 0.294 & 0.491\\
0.1 \% & 0.375 & 0.556\\
\end{tabular}
\caption{QCL thresholds obtained after 1000 permutations}
\label{permutations}
\end{table}
